\chapter*{Scientific Panel}

\begin{multicols}{2}

\small


%\emindSubtitle{Executive Editor}

%\volumeEntry{Dr. Martín González-Rodríguez}
%{University of Oviedo.\\
%The Human Communication and Interaction Research Group.\\
%Departamento de Informática.\\
%Calvo Sotelo s/n\\
%33007 - Oviedo.\\
%Spain.
%}


%\emindSubtitle{Volume Editors}

%\volumeEntry{Fidel Díez Díaz}
%{University of Oviedo.\\
%The Human Communication and Interaction Research Group.\\
%Departamento de Informática.\\
%Calvo Sotelo s/n\\
%33007 - Oviedo.\\
%Spain.
%}

%\volumeEntry{Jorge Manrubia Díez}
%{Ministerio de Trabajo y Asuntos Sociales.\\
%Gerencia de Informática de la Seguridad Social.\\
%Albasanz 26\\
%Madrid - 28037.\\
%Spain.
%}


%\emindSubtitle{Section Editors}

%\volumeEntry{Jaime García Marsa}
%{Legendarya I+D.\\
%Avda. Gral. Capalleja, 27\\
%33873 - Navelgas.\\
%Spain.
%}

%\volumeEntry{Javier Pisano}
%{University of Oviedo.\\
%The Human Communication and Interaction Research Group.\\
%Departamento de Informática.\\
%Calvo Sotelo s/n\\
%33007 - Oviedo.\\
%Spain.
%}

%\volumeEntry{Cristobal Rivera Rodríguez}
%{University of Oviedo.\\
%The Human Communication and Interaction Research Group.\\
%Departamento de Informática.\\
%Calvo Sotelo s/n\\
%33007 - Oviedo.\\
%Spain.
%}

%\newpage

%\emindSubtitle{Editorial Board}


\volumeEntry{Dr. Alecia E. Acosta Freites}{
Centro ISYS.\\
Escuela de Computación.\\
Facultad de Ciencias.\\
Universidad Central de Venezuela.\\
Caracas.\\
Venezuela.}

\volumeEntry{Dr. Tomohiro Amemiya}{
NTT Comunication Science Laboratories.\\
3-1 Morinosato Wakamiya. Atsugi-shi.\\
Kanagawa Pref. 243-0198.\\
Japan.}

\volumeEntry{Dipl.-Ing. Kerstin Altmanninger}
{Johannes Kepler University Linz.\\
Department of Telecooperation.\\
Altenberger Str. 69.\\
4040 Linz.\\
Austria.
}

\volumeEntry{Dr. Ian D. Benest}{
Department of Computer Science.\\
University of York.\\
Heslington.\\ 
York, YO10 5DD.\\
United Kingdom.}

\volumeEntry{Dr. Udo Bleimann}{
University of Applied Sciences.\\
Fachhochschule Darmstadt.\\
Fachbereich Informatik.\\
Schöfferstrasse 8b.\\
D-64295 Darmstadt.\\
Germany.
}

\volumeEntry{Dr. Peter Bodrogi}{
University of Pannonia.\\
Department of Image Processing and Neurocomputing.\\ 
Egyetem u. 10.\\
H-8200, Veszprem.\\ 
Hungary.
}

\columnbreak

\volumeEntry{Dr. Oliver Brdiczka}{
Palo Alto Research Center (PARC).\\
Computer Science Laboratory (CSL).\\
3333 Coyote Hill Road.\\
Palo Alto, CA, 94304.\\
USA.}

\volumeEntry{Dr. Cesar A. Collazos O.}
{Universidad de Cauca.\\
System Department - FIET.\\
Sector Tulcan.\\
Popayán.\\
Colombia.
}

\volumeEntry{Dr. John Darzentas}{
University of the Aegean.\\
Product and Systems Design Engineering.\\
Syros.\\ 
Greece.
}

\volumeEntry{Dr. Paul Dowland}{
University of Plymouth.\\
Network Research Group.\\
School of Computing, Communications and Electronics.\\
Room A304 Portland Square.\\
Drake Circus.\\
Plymouth PL4 8AA.\\
United Kingdom.
}


\volumeEntry{Dr. Christos Fidas}
{Human-Computer Interaction Group.\\
University of Patras.\\
GR-26500 Rio Patras.\\
Greece.
}

\columnbreak

\volumeEntry{Dr. Pablo A. Figueroa}{
Of. W313. Departamento de Ingenieria de Sistemas y Computación.\\
Universidad de los Andes.\\
Carrera 1 18A 10.\\
Bogota. Colombia.
}

\volumeEntry{Dr. Steven Furnell}
{University of Plymouth.\\
Network Research Group.\\
School of Computing, Communications and Electronics.\\
Room A304 Portland Square.\\
Drake Circus.\\
Plymouth PL4 8AA.\\
United Kingdom.
}

%\volumeEntry{MSE. Fabien Girardin}{
%Center for Research and Support of Training and its Technologies.\\
%Swiss Federal Institute of Technology Lausanne.\\
%CH-1015 Lausanne.\\     
%Switzerland.}


\volumeEntry{Dr. Patrícia C. T. Goncalves}
{Mechanical Engineering and Industrial Management Institute.\\
Faculty of Engineering.\\
University of Porto.\\
Rua Roberto Frias, 4200-465 Porto.\\
Portugal.}

\volumeEntry{Victor M. Gonzalez}{
Manchester Business School.\\
University of Manchester.\\
United Kingdom.
}

\columnbreak

%\volumeEntry{Dr. Lisbeth Harms}{
%University of Copenhagen.\\
%Department of Psychology.\\
%Oester Farimagsgade 5,\\
%K 2353.\\
%Copenhagen.\\
%Denmark.
%}


\volumeEntry{MSE. Sven Hartrumpf}{
Intelligent Information and Communication Systems (IICS).\\
Department of Mathematics and Computer Science.\\
FernUniversität in Hagen.\\
58084 Hagen.\\
Germany.
}


%\volumeEntry{Dr. Wilko Heuten}{
%OFFIS Institute für Informatik.\\
%Escherweg 2.\\
%26121 Oldenburg.\\
%Germany.
%}

\volumeEntry{Dr. Rachid Kadouche}{
Laboratotrie DOMUS.\\
Département d'informatique.\\
Faculté des sciences.\\
Université de Sherbrooke.\\
2500 boul. Université.\\
Sherbrooke, QC.\\
Canada, J1K 2R1.
}


\volumeEntry{MSE. Zsolt T. Kardkovács}
{Budapest University of Technology and Economics.\\
Department of Telecommunications and Media Informatics.\\
H-1117, Budapest, Magyar tudósok körútja 2. L109.\\
Budapest.\\
Hungary.
}

\columnbreak

\volumeEntry{Dr. Yoshihiro Kawahara}{
Asami Laboratory.\\
Dept. of EE Eng.\\
The University of Tokyo.\\
7-3-1 Hongo Bunkyo-ku, Tokyo.\\
University of Tokio.\\
Japan.
}


\volumeEntry{Dr. HyungJun Kim}{
Hansei Assistive Technologies.\\
Division of Information Technology.\\
Hansei University.\\
604-5 Dangjung Gunpo Kyunggi 435-742.\\
Korea.}



\volumeEntry{Dr. Chris Kimble}{
Department of Computer Science.\\
University of York.\\
Heslington.\\ 
York, YO10 5DD.\\
United Kingdom.}

\volumeEntry{Dr. Daniel Kuen Seong Su}
{School of Computer Science.\\
The University of Nottingham.\\
Jalan Broga, 43500, Semenyih.\\
Selangor Darul Ehsan.\\
Malaysia.}

\volumeEntry{MSE Anil Kumar}{
Patni Computer Systems Ltd.\\
Logix Park, Sec. 16.\\
Noida, UP, 201301.\\
India.\\
}

\columnbreak

\volumeEntry{Dr. Cecilia Lányi}{
University of Pannonia.\\
Department of Image Processing and Neurocomputing.\\ 
Egyetem u. 10.\\
H-8200, Veszprem.\\ 
Hungary.
}

\volumeEntry{MA Irene Mavrommati}
{Computer Technology Institute.\\
Kazantzaki str.\\
University Campus.\\
26500 Patras.\\
Greece.
}

%\volumeEntry{Dr. Guido Menkhaus}{
%Managing Director Aida.\\
%Hochschule Darmstadt - University of Applied Sciences.\\
%Institute of Applied Informatics Darmstadt.\\
%Haardtring 100.\\ 
%D-64295 Darmstadt.\\
%Germany.}

\volumeEntry{Dr. Permanand Mohan}
{University of the West Indies.\\
Department of Mathematics and Computer Science.\\
Augustine.\\
Trinidad and Tobago.
}



\volumeEntry{Dr. Chang S Nam}{
Assistant Professor Department of Industrial Engineering.\\
University of Arkansas.\\
USA.
}




\volumeEntry{Dr. Janni Nielsen}
{Copenhagen Business School.\\
Department of Informatics.\\
Howitzvej 60, DK - 2000 Frederiksberg.\\
Copenhagen.\\
Denmark.
}

\columnbreak

\volumeEntry{Dr. Muhammad Shafie Abd Latiff}{
Department of Computer Systems and Communications.\\
Faculty of Computer Science and Information System.\\
Universiti Teknologi Malaysia.\\
81310 UTM Skudai, Johor.\\
Malaysia.}

\volumeEntry{Dr. Martin Schrepp}{
SAP AG.\\
Dietmar-Hopp-Alle 16.\\
69190 Walldorf.\\
Germany.}

%\volumeEntry{MSE. Muhammad Shafie Abd Latiff}{
%Financial Services.\\
%Accenture.\\
%Level 66, Tower 2, KLCC.\\
%50088 Kuala Lumpur.\\
%Malaysia.}

%\volumeEntry{Victoria Siew Yen Yee}{
%Consultant, Industry and Functional Solution.\\
%Accenture.\\
%Malaysia.
%}


\volumeEntry{MSE. Dipak Surie}{
Room number D418, MIT Huset.\\
Umeå University.\\
S-901 87 Umeå.\\     
Sweden.}

%\volumeEntry{MSE. Daniel Szabo}{
%Escuela de Tecnología.\\
%Facultad de Ingeniería.\\
%ORT University.\\
%Curey 1451.\\
%11.100, Montevideo.\\
%Uruguay.}

\volumeEntry{Dr. Hiroshi Tamura}{
R+D Division, Hakuhodo Inc.\\
4-1 Shibaura 3-Chome, Minato-Ku.\\
108-8088, Tokyo.\\ 
Japan.}

\volumeEntry{Dr. Joao Manuel R. S. Tavares}{
Mechanical Engineering and Industrial Management Institute.\\
Faculty of Engineering.\\
University of Porto.\\
Rua Roberto Frias, 4200-465 Porto.\\
Portugal.}


%\volumeEntry{MSE. Kenji Terabayashi}{
%Dept. of Precision Mechanics.\\
%Chuo University.\\
%1-13-27 Kasuga, Bunkyo-ku.
%Tokyo 112-8551.\\
%Japan.}


\volumeEntry{Dr. Lorna Uden}
{Staffordshire University.\\
School of Computing.\\
The Octagon, Beaconside.\\
Stafford, ST18 0AD.\\
United Kingdom.
}


\volumeEntry{MSE. Daniela Villani}{
ICE-NET Lab.\\
Universita Cattolica del Sacro Cuore.\\
Largo Gemelli 1, 20100 Milan.\\
Italy.
}

\volumeEntry{Dr. Lionel Villard}{
IBM T. J. Watson Research Center.\\
PO Box 704.\\
Yorktown Heights, NY 10598-0704.\\
USA.
}


\volumeEntry{Dr. Krzysztof Walczak}
{The Poznan University of Economics.\\
Department of Information Technology.\\
ul. Mansfelda 4.\\
Poznan 60-854.\\
Poland.
}

\volumeEntry{Dr. Paul Walsh}{
Department of Maths and Computing.\\
Cork Institute of Technology.\\
Rossa Avenue.\\
Bishopstow, Cork.\\
Ireland.}

\volumeEntry{Dr. Wojciech Wiza}
{The Poznan University of Economics.\\
Department of Information Technology.\\
ul. Mansfelda 4.\\
Poznan 60-854.\\
Poland.
}

\volumeEntry{Dr. Wolfram Wöß}
{Johannes Kepler University Linz.\\
Institute for Applied Knowledge Processing.\\
Altenberger Str. 69.\\
4040 Linz.\\
Austria.
}

\newpage

\end{multicols}



\normalsize

