
\volumeEntry{Dr Muhammad Shafie Abd Latiff}{
Universiti Teknologi Malaysia\\
Faculty of Computer Science and Information System\\
81310 Skudai\\
Johor\\
Malaysia
}


\volumeEntry{Dr Alecia Eleonora Acosta Freites}{
Central University of Venezuela\\
Av. Los ilustres\\
Facultad  de Ciencias, Escuela de Computación\\
Centro ISYS\\
Caracas, 1041A\\
Venezuela
}


\volumeEntry{Dipl.-Ing. Kerstin Altmanninger}{
Johannes Kepler University Linz\\
Altenberger Straße 69\\
4040 Linz\\
Austria
}


\volumeEntry{Dr. Tomohiro Amemiya}{
NTT Communication Science Laboratories\\
3-1 Morinosato Wakamiya\\
Atsugi\\
Kanagawa, 243-0198\\
 Japan
}


\volumeEntry{Dr Ian Benest}{
University of York\\
Department of Computer Science\\
Heslington\\
York, YO10 5DD\\
United Kingdom
}


\volumeEntry{Prof. Dr. Udo Bleimann}{
University of Applied Sciences Darmstadt\\
Haardtring 100\\
D-64295 Darmstadt\\
Germany
}


\volumeEntry{Dr. Oliver Brdiczka}{
Palo Alto Research Center (PARC)\\
3333 Coyote Hill Road\\
Palo Alto, CA, 94304\\
United States of America
}


\volumeEntry{Dr. Cesar Collazos O.}{
University of Cauca\\
System Department - FIET\\
Sector Tulcan\\
Carrera 7A No.19N17\\
Popayán\\
Colombia
}


\volumeEntry{MSE David Correa}{
EUITIO - UNIOVI\\
C. Valdés Salas 13\\
Oviedo, Asturias\\
33007\\
España
}


\volumeEntry{Dr. Christos Fidas}{
University of Patras\\
Ipatias Street\\
26500 Rio, Patras
\\Greece
}


\volumeEntry{Prof. Pablo Figueroa}{
Universidad de los Andes\\
Of. ML 434\\
Carrera 1 - 18A 10\\
Bogotá\\
Colombia
}


\volumeEntry{Prof. Steven Furnell}{
University of Plymouth\\
Drake Circus\\
Plymouth\\
United Kingdom
}


\volumeEntry{Ms. Patrícia Gonçalves}{
Faculty of Engineering of the University of Porto\\
INEGI\\
Campus FEUP\\
Rua Roberto Frias, 400\\
4200-465 Porto\\
Portugal
}


\volumeEntry{Dr. Victor Gonzalez}{
University of Manchester\\
Manchester Business School\\
MBS East Room F 40, Booth Street East\\
Manchester, UK, M13 9SS\\
United Kingdom
}


\volumeEntry{Dra. María Gonzalez Azconegui}{
National Council of Scientific and Technical Research (CONICET) and Universidad Nacional del Sur\\
Dpto de Ciencias e Ing de la Computación\\
Universidad Nacional del Sur\\
Av Alem 1253\\
8000 - Bahia Blanca\\
Argentina
}


\volumeEntry{Dr. Sven Hartrumpf}{
FernUniversität in Hagen\\
Prakt. Informatik VII \\
Hagen\\
Germany
}


\volumeEntry{Dr Rachid Kadouche}{
DOMUS Sherbrooke\\
Département d'informatique\\
Faculté des sciences\\
Université de Sherbrooke\\  
2500 boulevard de l'Université\\
 J1K 2R1 Sherbrooke, Québec\\
Canada
}


\volumeEntry{Dr. Yoshihiro Kawahara}{
The University of Tokio\\
7-3-1 Hongo Bunkyo-ku Tokyo\\ 113-8656\\
Japan
}


\volumeEntry{Dr. HyungJun Kim}{
Hansei University\\
Division of Information Technology\\
604-5 Dangjung-dong Gunpo-si\\
Kyunggi-do 435-742\\
Republic of Korea
}


\volumeEntry{M. Chris Kimble}{
Euromed Marseille École de Management\\
Domaine de Luminy, BP 921,\\
13288, Marseille Cedex 9,\\
France
}


\volumeEntry{Mr. Anil Kumar}{
Patni Americas Inc.\\
1626, 9th st\\
apt 102, White Bear Lake\\
 MN, 55110\\
United States of America
}


\volumeEntry{Dr Cecilia Lányi}{
University of Pannonia\\
VIRT\\
Egyetem u. 10.\\
Veszprem\\
H-8200\\
Hungary
}


\volumeEntry{Ms Irene Mavrommati}{
Hellenic Open University\\
Nafsikas 73\\
26442 Patras\\
Greece
}


\volumeEntry{Dr. Permanand Mohan}{
The University of the West Indies\\
Department of Mathematics and Computer Science\\
St. Augustine\\
Trinidad and Tobago
}


\volumeEntry{Dr. Chang Nam}{
University of Arkansas\\
4207 Bell Engineering Center\\
Fayetteville, AR 72701\\
United Sates of America
}


\volumeEntry{Professor Janni Nielsen}{
Copenhagen Business School\\
CAICT\\ 
Howitzvej 60\\ 
DK 2000 Frederiksberg\\ 
Denmark
}


\volumeEntry{Dr. Martin Schrepp}{
SAP AG\\
Dietmar-Hopp-Allee 16\\
69190 Walldorf\\
Germany
}


\volumeEntry{Mr. Daniel Su}{
The University of Nottingham\\
School of Computer Science,\\
Faculty of Science,\\
Jalan Broga,\\
43500 Semenyih,\\
Selangor Darul Ehsan,\\
Malaysia.
}


\volumeEntry{MSE Dipak Surie}{
Umeå University\\
Department of computing science\\
S-901 87 Umeå\\
Sweden
}


\volumeEntry{MSE Hiroshi Tamura}{
Hakuhodo Inc.\\
4-1 Shibaura 3-Chome\\
Minato-Ku\\
Tokyo 108-8088\\
 Japan
}


\volumeEntry{Prof. Joao Manuel Tavares}{
University of Porto\\
Prof. João Manuel R. S. Tavares\\
Faculdade de Engenharia da Universidade do Porto\\
(DEMEGI - SDI)\\
Rua Dr. Roberto Frias, s/n\\
4200-465 Porto\\
Portugal
}


\volumeEntry{PhD Daniela Villani}{
Catholic University of Milan\\
Largo Gemelli 1\\
20100 Milan\\
Italy
}


\volumeEntry{Dr Lionel Villard}{
IBM T. J. Watson Research Center\\
19 Skyline Dr\\
Hawthorne, NY 10598\\
United States of America
}


\volumeEntry{Dr. Krzysztof Walczak}{
Poznan University of Economics\\
Department of Information Technology\\
Mansfelda 4, 60-854 Poznan\\
Poland
}


\volumeEntry{Dr Paul Walsh}{
Cork Institute of Technology\\
Department of Computing\\
Bishopstown\\
Cork\\
Ireland
}


\volumeEntry{Prof. Dr. Wolfram Wöß}{
Johannes Kepler University Linz\\
Altenberger Str. 69\\
A-4040 Linz\\
Austria
}


\volumeEntry{Dr Wojciech Wiza}{
Poznan University of Economics\\
ul.Mansfelda 4\\
60-854 Poznan\\
Poland
}

